Presentation Plan\\ FF-Replan: \& RFF\@: Exploiting classical AI planning for uncertain and probabilistic domains

### 2014-03-08 presentation-plan/Plan_presentation_monday.tex
Add some examples of applications of planning problems

\begin{itemize}
	\item Blocks World
	\item Motion Planning
\end{itemize}

@@

>>>>

\begin{itemize}
	\item Blocks World
	\item Motion Planning
	\item Inventory Management~\cite{puterman2009markov}
	\item Equipment Maintenance~\cite{puterman2009markov}
	\item Communication Models~\cite{puterman2009markov}
\end{itemize}

@@

\subsubsection{Inventory Management} How much of X do we need to order from the
supplier every day until the end of the season?

\subsubsection{Equipment Maintenance} A bus company is responsible for keeping
all buses in a good working condition. One aspect is when to replace the bus
engines~\cite{puterman2009markov}. This problem could be represented as a
MDP\@.  When to schedule disruptive maintenance jobs by their deadline?

\subsubsection{Communication Models} Many computer, manufacturing and
communication systems can be modelled as networks with waiting queues and
servers. Systems have receiving packages, routing, and varying service rates.
